\documentclass{article}

\usepackage{amsmath} % For advanced math features
\usepackage{amsfonts} % For mathematical fonts
\usepackage{amssymb} % For symbols

\begin{document}

\title{Statistical Formulas}
\author{Your Name}
\date{\today}
\maketitle

\section{Introduction}

This document contains common statistical formulas used in data analysis and probability theory.

\section{Mean (Average)}
The arithmetic mean of a dataset \(x_1, x_2, \dots, x_n\) is given by:

\[
\bar{x} = \frac{1}{n} \sum_{i=1}^{n} x_i
\]

Where:
- \( \bar{x} \) is the sample mean.
- \( n \) is the number of data points.

\section{Variance}
The variance of a dataset measures the spread of the data. The formula for the population variance \(\sigma^2\) is:

\[
\sigma^2 = \frac{1}{N} \sum_{i=1}^{N} (x_i - \mu)^2
\]

Where:
- \( \sigma^2 \) is the population variance.
- \( N \) is the number of data points.
- \( \mu \) is the population mean.

For sample variance \(s^2\), the formula is:

\[
s^2 = \frac{1}{n-1} \sum_{i=1}^{n} (x_i - \bar{x})^2
\]

Where \( \bar{x} \) is the sample mean.

\section{Standard Deviation}
The standard deviation is the square root of the variance. The formula for the population standard deviation \(\sigma\) is:

\[
\sigma = \sqrt{\frac{1}{N} \sum_{i=1}^{N} (x_i - \mu)^2}
\]

For sample standard deviation \(s\), the formula is:

\[
s = \sqrt{\frac{1}{n-1} \sum_{i=1}^{n} (x_i - \bar{x})^2}
\]

\section{Correlation}
The correlation coefficient between two variables \(X\) and \(Y\) is given by:

\[
r = \frac{\sum_{i=1}^{n} (x_i - \bar{x})(y_i - \bar{y})}{\sqrt{\sum_{i=1}^{n} (x_i - \bar{x})^2 \sum_{i=1}^{n} (y_i - \bar{y})^2}}
\]

Where:
- \(r\) is the Pearson correlation coefficient.
- \(x_i\) and \(y_i\) are the data points for variables \(X\) and \(Y\), respectively.
- \( \bar{x} \) and \( \bar{y} \) are the means of \(X\) and \(Y\).

\section{Linear Regression}
The equation for a simple linear regression line is:

\[
y = \beta_0 + \beta_1 x
\]

Where:
- \(y\) is the dependent variable.
- \(x\) is the independent variable.
- \(\beta_0\) is the intercept.
- \(\beta_1\) is the slope of the line.

The formulas for calculating \(\beta_0\) and \(\beta_1\) are:

\[
\beta_1 = \frac{n \sum_{i=1}^{n} x_i y_i - \sum_{i=1}^{n} x_i \sum_{i=1}^{n} y_i}{n \sum_{i=1}^{n} x_i^2 - \left(\sum_{i=1}^{n} x_i\right)^2}
\]

\[
\beta_0 = \bar{y} - \beta_1 \bar{x}
\]

Where:
- \( \bar{x} \) and \( \bar{y} \) are the means of the variables \(x\) and \(y\), respectively.

\end{document}
